Dear Reviewers,

We appreciate your time and effort in reviewing our work. Thanks to your constructive comments and insightful suggestions, we have made the following changes to the manuscript:
\begin{itemize}
    \item{%
        Heavily modified Section~IV to better present the applicability and benefits of the proposed \emph{discrete-time} passive-systems interpretation of the gradient descent (GD) method. 
    }%
    \item{%
        Due to space constraints, we have removed the discussion around the gain-scheduling interpretation of the GD method with time-varying step size using scheduling functions that are Kronecker delta functions. Instead, Section~IV-B of the revised manuscript now focuses on the proposed gain-scheduled modified GD controller in Figure~5.
    }%
    \item{%
        A new GD stopping criterion based on the results of the weak passivity theorem is now explicitly proposed in Section~IV-A.
    }%
    \item{%
        Expanded the introduction to include the input-output stability guarantees resulting from the weak and strong version of the passivity theorems. 
    }%
    \item{%
        Modified the title, abstract, introduction, and closing remarks to highlight that we consider the \emph{discrete-time} passivity-based analysis of the GD method.
    }%
    
\end{itemize}
Below, we have addressed your specific comments and suggestions. Within comments/responses, the citation numbers refer to the References section on page \pageref{endofcontent}. We have also appended the revised manuscript with the major changes highlighted in \textcolor{magenta}{magenta}.

We believe that our contributions are now more clearly presented, and the results are more thorough. 

Thank you for helping us improve the quality of our work.



Sincerely,\\[1em]%
\theauthor